### 2020-05-13 README.Rmd
New README

<!-- badges: start -->
<!-- badges: end -->

The goal of eurobarometer is to ...

@@

At this moment yuo cannot install yest the packgae from [CRAN](https://CRAN.R-project.org), but there is a development version on [GitHub](https://github.com/):

@@

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/antaldaniel/eurobarometer/branch/master/graph/badge.svg)](https://codecov.io/gh/antaldaniel/eurobarometer?branch=master)
[![Project Status: Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
"[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)"
"[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/regions)](https://cran.r-project.org/package=eurobarometer)"
<!-- badges: end -->

The goal of eurobarometer is converting Eurobarometer microdata files, as stored by GESIS, into tidy R data frames and help common pre-processing problems.

Please report all issues to [github.com/antaldaniel/eurobarometer/issues](https://github.com/antaldaniel/eurobarometer/issues).

Pull requests are welcome on [github.com/antaldaniel/eurobarometer]((https://github.com/antaldaniel/eurobarometer/issues))  from all potential contributors who abide by  the terms of the [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).

@@

At this moment you cannot install yest the packgae from [CRAN](https://CRAN.R-project.org), but there is a development version on [GitHub](https://github.com/):

@@

## Code of Conduct

Please note that the eurobarometer project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to its terms.
